### 2015-02-18 fundamentals/examples.tex
using the glossary

\begin{enumerate}
    \item Once through (no recycle)
    \item 1-pass MOX recycle
    \item Infinite-pass MOX recycle
\end{enumerate}

@@

    \item \textbf{Reactor} (\Class{cycamore::Reactor}): This is a reactor
        model that requests any number of input fuel types and transmutes them
        to static compositions when they are burnt and discharged from the
        core.  . The reactor was configured to model a light water reactor
        with a 3 batch core (20,000 kg HM per batch) operating on an 18 month
        cycle with a 2 month refuel time.  The reactor was also configured to
        take in either enriched UOX fuel or recycled MOX fuel.

    \item \textbf{Recycled Fuel Fabrication} (\Class{cycamore::Fab}): This
        facility requests depleted uranium and separated fissile material and
        mixes them together into recycled MOX fuel that it offers to
        requesters.  The two streams are mixed in a ratio in order to match
        simple neutronics properties of the target fuel as closely as
        possible.  The method used is based on a variation "equivalence
        method" originally developed by Baker and Ross
        \cite{baker_comparison_1963}.  This technique has also been used in the
        \gls{COSI} fuel cycle simulator developed by the French \gls{CEA}.

@@

Modifying the input file specification to model each of the 3 fuel cycles was
done by making simple adjustments to the commodities and trade preferences for
each of the facilities.  The reactor was configured to request recycled MOX
fuel with a higher preference then new \gls{UOX} fuel. For the once through case,
the \Class{Reactor} was set to offer all spent fuel as waste.  For the 1-pass
recycle case, the \Class{Reactor} offered spent \gls{UOX into a spent fuel market,
but spent MOX is still offered as waste.  In the infinite-pass recycle case,
the \Class{Reactor} offers all burned fuel into a spent fuel market. The
separations facility requests spent fuel with a higher preference than the
repository resulting in preferential recycle.  All these preferences are easy
to adjust and \Cyclus dynamically handles supply constraints and non-uniform
preference resolution.  It is notable that separations and recycle fuel
fabrication capacity are deployed identically in all simulations.  In the once
through case, the recycling loop never acquires material, and so reactors
always receive fresh \gls{UOX} fuel.  The \gls{DRE} ensures everything operates
smoothly in all cases.

>>>>

\begin{enumerate}
    \item Once through (no recycle)
    \item 1-pass \gls{MOX} recycle
    \item Infinite-pass \gls{MOX} recycle
\end{enumerate}

@@

    \item \textbf{Reactor} (\Class{cycamore::Reactor}): This is a reactor
        model that requests any number of input fuel types and transmutes them
        to static compositions when they are burnt and discharged from the
        core.  . The reactor was configured to model a light water reactor
        with a 3 batch core (20,000 kg HM per batch) operating on an 18 month
        cycle with a 2 month refuel time.  The reactor was also configured to
        take in either enriched \gls{UOX} fuel or recycled \gls{MOX} fuel.

    \item \textbf{Recycled Fuel Fabrication} (\Class{cycamore::Fab}): This
        facility requests depleted uranium and separated fissile material and
        mixes them together into recycled \gls{MOX} fuel that it offers to
        requesters.  The two streams are mixed in a ratio in order to match
        simple neutronics properties of the target fuel as closely as
        possible.  The method used is based on a variation "equivalence
        method" originally developed by Baker and Ross
        \cite{baker_comparison_1963}.  This technique has also been used in the
        \gls{COSI} fuel cycle simulator developed by the French \gls{CEA}.

@@

Modifying the input file specification to model each of the 3 fuel cycles was
done by making simple adjustments to the commodities and trade preferences for
each of the facilities.  The reactor was configured to request recycled \gls{MOX}
fuel with a higher preference then new \gls{UOX} fuel. For the once through case,
the \Class{Reactor} was set to offer all spent fuel as waste.  For the 1-pass
recycle case, the \Class{Reactor} offered spent \gls{UOX} into a spent fuel market,
but spent \gls{MOX} is still offered as waste.  In the infinite-pass recycle case,
the \Class{Reactor} offers all burned fuel into a spent fuel market. The
separations facility requests spent fuel with a higher preference than the
repository resulting in preferential recycle.  All these preferences are easy
to adjust and \Cyclus dynamically handles supply constraints and non-uniform
preference resolution.  It is notable that separations and recycle fuel
fabrication capacity are deployed identically in all simulations.  In the once
through case, the recycling loop never acquires material, and so reactors
always receive fresh \gls{UOX} fuel.  The \gls{DRE} ensures everything operates
smoothly in all cases.
